Development of restored dike grasslands to reference needs more than four years and can hardly modified by local site conditions

### 2023-01-27 manuscript.Rmd
Finish figure captions

The seed mixture-substrate combination were tested with an experiment on a dike of the River Danube in SE Germany, which was established in March 2018 (Figure \@ref(fig:figure-map)); 314 m above sea level; WGS84 (lat/lon), 48.83895, 12.88412). The climate is temperate-suboceanic with a mean annual temperature of 8.4 °C and an annual precipitation of 984 mm [@dwd2021]. During the study, three exceptionally dry years (2018--2020) occurred [@hari2020; @cdc2022temp; @cdc2022prec], and three minor floods which did not reach the plots [Appendix Table \@ref(tab:flood-weather), @lfu2021waterlevel; @lfu2021discharge]. Regional sand (0--4 mm) was used to lean the substrate and the soil was taken from the dike<!--# Is that right?  --> and a with an excavator the substrates were mixed <!--# Is that right?  --> and the plots prepared. The target vegetation were lowland hay meadows (Arrhenatherion elatioris, CM01A) and calcareous grassland [Cirsio-Brachypodion pinnati, DA01B code of the EuroVegChecklist, @mucina2016]. The species pool of hay meadows and calcareous grasslands consisted of 55 and 58 species , respectively. The seeds were received from a commercial producer of autochtonous seeds. From the species pools, 20 species were randomly selected for each plot. The seed mixtures always contained seven grasses (60 wt% of total seed mixture), three legumes (5%) and ten herbs (35%) (Table \@ref(tab:seedmix)). The community-weighted means (CWM) of functional traits differed between the seed mixture types (Table \@ref(tab:traits)) . The management started with a cut without hay removal and a mowing height of 20 cm in August 2018, followed by 'normal' deep cuts with hay removal in July 2019 and 2020. In October 2018, Bromus hordeaceus was seeded as a nursery grass to provide safe sites under drought conditions.

@@

To measure the effects of the treatments on our three response variables, we calculated Bayesian linear mixed effects models (BLMM) with the random effect plot nested in block with the Cauchy prior [see @lemoine2019]. Furthermore, we included as a fixed effect the botanists of each plot. For the simple effects of the treatments, we chose plausible weakly informative priors. To evaluate the influence of the priors, prior predictive checks and models with non-informative priors were calculated. For the computation, we used 4 chains, a thinning rate of 2, 5,000 iterations for warm-up and 10,000 in total. For evaluating the computation, MCMC chain convergence was checked with trace plots and by the R-hat values and MCMC chain resolution by the effective sampling size (ESS). Posterior predictive check was done with Kernel density estimates histograms of statistics skew and leave-one-out (LOO) cross-validation [see @gabry2019]. Finally, models were compared with the Bayes factor (BF) and Bayesian *R*² values [@gelman2019].

@@

Each plot received an individual set of 20 species with some restrictions to the number of species per functional group. The total species pool for hay meadows was 55 and for calcareous grassland 58. In total, seed mixtures had 16 or 32 g per plot.

```{r table-seedmix, tab.id = "seedmix", tab.cap = "Seedmix"}
read_csv(here::here("data", "raw", "data_raw_table_1_seedmix.csv"),
         show_col_types = FALSE) %>%
  slice(-1) %>%
  flextable() %>%
  merge_at(part = "header", j = 2:3) %>%
  align(align = "center", part = "all") %>%
  align(align = "left", part = "all", j = 1) %>%
  add_header_row(top = FALSE, values = c("", "Hay meadow", "Calcareous grassland", "", "", "")) %>%
  add_header_row(top = FALSE, values = c("", "#", "#", "#", "%", "%")) %>%
  bold(part = "header", i = 1) %>%
  autofit()
```

@@

```{r figure-map, fig.cap = "Map", fig.asp = 1.2854, fig.width = 5}
knitr::include_graphics(here::here("outputs", "figures", "figure_1_map.png"))
```

The experiment was located

@@

```{r fig.id = "figure-effects", fig.cap = "Effects", fig.asp = 0.3030, fig.width = 6.49}
knitr::include_graphics(here::here("outputs", "figures", "figure_2_800dpi_16.5x5cm.tiff"))
```

@@

```{r fig.id = "figure-persistence", fig.cap = "Persistence", fig.asp = 0.4848, fig.width = 6.49}
knitr::include_graphics(here::here("outputs", "figures", "figure_3_persistence_epred_800dpi_16.5x8cm.tiff"))
```

@@

```{r fig.id = "figure-fcs", fig.cap = "Favourable Conservation Status (FCS)", fig.asp = 0.4848, fig.width = 6.49}
knitr::include_graphics(here::here("outputs", "figures", "figure_4_fcs_epred_800dpi_16.5x8cm.tiff"))
```

@@

```{r fig.id = "figure-recovery", fig.cap = "Recovery", fig.asp = 0.4848, fig.width = 6.49}
knitr::include_graphics(here::here("outputs", "figures", "figure_5_recovery_epred_800dpi_16.5x8cm.tiff"))
```

Fig. 5:

@@

```{r fig.id = "figure-nmds", fig.cap = "NMDS", fig.asp = 0.9696, fig.width = 6.49}
knitr::include_graphics(here::here("outputs", "figures", "figure_6_nmds_800dpi_16.5x16cm.tiff"))
```

Fig. 6:

>>>>

The seed mixture-substrate combination were tested with an experiment on a dike of the River Danube in SE Germany, which was established in March 2018 (Figure \@ref(fig:figure-map)); 314 m above sea level; WGS84 (lat/lon), 48.83895, 12.88412). The climate is temperate-suboceanic with a mean annual temperature of 8.4 °C and an annual precipitation of 984 mm [@dwd2021]. During the study, three exceptionally dry years (2018--2020) occurred [@hari2020; @cdc2022temp; @cdc2022prec], and three minor floods which did not reach the plots [Appendix Table @ref(tab:flood-weather), @lfu2021waterlevel; @lfu2021discharge]. Regional sand (0--4 mm) was used to lean the substrate and the soil was taken from the dike<!--# Is that right?  --> and a with an excavator the substrates were mixed<!--# Is that right?  --> and the plots prepared. The target vegetation were lowland hay meadows [EUNIS code: R22, @Chytry.2020; Arrhenatherion elatioris, EuroVegChecklist: CM01A, @mucina2016] and semi-dry calcareous grassland (R1A; Cirsio-Brachypodion pinnati, DA01B). The species pool of hay meadows and dry grasslands consisted of 55 and 58 species, respectively. The seeds were received from a commercial producer of autochtonous seeds. From the species pools, 20 species were randomly selected for each plot. The seed mixtures always contained seven grasses (60 wt% of total seed mixture), three legumes (5%) and ten herbs (35%) (Table \@ref(tab:seedmix)). The community-weighted means (CWM) of functional traits differed between the seed mixture types (Table \@ref(tab:traits)) . The management started with a cut without hay removal and a mowing height of 20 cm in August 2018, followed by 'normal' deep cuts with hay removal in July 2019 and 2020. In October 2018, Bromus hordeaceus was seeded as a nursery grass to provide safe sites under drought conditions.

@@

To measure the effects of the treatments on our three response variables, we calculated Bayesian linear mixed-effects models (BLMM) with the random effect plot nested in block with the Cauchy prior [see @lemoine2019]. Furthermore, we included as a fixed effect the botanists of each plot. For the simple effects of the treatments, we chose plausible weakly informative priors. To evaluate the influence of the priors, prior predictive checks and models with non-informative priors were calculated. For the computation, we used 4 chains, a thinning rate of 2, 5,000 iterations for warm-up and 10,000 in total. For evaluating the computation, MCMC chain convergence was checked with trace plots and by the R-hat values and MCMC chain resolution by the effective sampling size (ESS). Posterior predictive check was done with Kernel density estimates histograms of statistics skew and leave-one-out (LOO) cross-validation [see @gabry2019]. Finally, models were compared with the Bayes factor (BF) and Bayesian *R*² values [@gelman2019].

@@

Each plot received an individual set of 20 species with some restrictions to the number of species per functional group. The total species pool for hay meadows was 55 and for dry grassland 58. In total, seed mixtures had 16 or 32 g per plot.

```{r table-seedmix, tab.id = "seedmix", tab.cap = "Seedmix"}
read_csv(here::here("data", "raw", "data_raw_table_1_seedmix.csv"),
         show_col_types = FALSE) %>%
  slice(-1) %>%
  flextable() %>%
  merge_at(part = "header", j = 2:3) %>%
  align(align = "center", part = "all") %>%
  align(align = "left", part = "all", j = 1) %>%
  add_header_row(top = FALSE, values = c("", "Hay meadow", "Dry grassland", "", "", "")) %>%
  add_header_row(top = FALSE, values = c("", "#", "#", "#", "%", "%")) %>%
  bold(part = "header", i = 1) %>%
  autofit()
```

@@

```{r figure-map, fig.asp = 1.2854, fig.width = 5, fig.cap = "The experiment was located on a dike at river Danube in SE Germany.  The 288 plots were allocated in six blocks (red squares on upper photo) and on the north and south exposition (central photo). Four treatments were conducted (Sand admixture, substrate depth, seeding density, seed mixture type (H, D)) . The western half of a block was with a shallow substrate depth for the blocks and within this half the substrates. The photo on the bottom shows one block from the side (Photo: Markus Bauer)."}
knitr::include_graphics(
  here::here("outputs", "figures", "figure_1_map.png")
  )
```

@@

```{r fig.id = "figure-effects", fig.asp = 0.3030, fig.width = 6.49, fig.cap = "The posterior density distributions (grey) of the treatments calculated over all four surveyed years. Furthermore, the median and the 66% and 95% credible intervals are shown. We evaluated the persistence of sown species (A), the Favourable Conservation Status (FCS; B) and the successional distance to reference (recovery; C). Note that the zero lines indicate that both levels have equal values. This means that hay meadows are closer to their reference than dry grasslands  (C)."}
knitr::include_graphics(
  here::here("outputs", "figures", "figure_2_800dpi_16.5x5cm.tiff")
  )
```

@@

```{r fig.id = "figure-persistence", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "Persistence of sown species on a dike experiment over the years. The substrates had different sand admixtures and different seed mixture types were sown. Per plot were 20 species sown. Shown are the posterior distributions, their medians and 95 % credible intervals derived from a Bayesian linear mixed-effects model (BLMM)."}
knitr::include_graphics(
  here::here("outputs", "figures", "figure_3_persistence_epred_800dpi_16.5x8cm.tiff")
  )
```

@@

```{r fig.id = "figure-fcs", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "The Favourable Conservation Status (FCS) of a dike experiment. The substrates had different sand admixtures and different seed mixture types were sown. The zero line indicate that target and non-target species are balanced. Positive values indicate that there are more target species.  Shown are the posterior distributions, their medians and 95 % credible intervals derived from a Bayesian linear mixed-effects model (BLMM)."}
knitr::include_graphics(
  here::here("outputs", "figures", "figure_4_fcs_epred_800dpi_16.5x8cm.tiff")
  )
```

@@

```{r fig.id = "figure-recovery", fig.asp = 0.4848, fig.width = 6.49, fig.cap = "The successional distance (d~jt,0~) of plots of a experiment on a dike to its respective reference sites (hay meadows or dry grasslands). The substrates had different sand admixtures and different seed mixture types were sown. The zero lines indicate the mean position of the reference sites on the NMDS axis 1 (@ref(fig:figure-nmds)). The grey area mark the standard deviation of the position of the reference sites. Shown are the posterior distributions, their medians and 95 % credible intervals derived from a Bayesian linear mixed-effects model (BLMM)."}
knitr::include_graphics(
  here::here("outputs", "figures", "figure_5_recovery_epred_800dpi_16.5x8cm.tiff")
  )
```

@@

```{r fig.id = "figure-nmds", fig.asp = 0.9696, fig.width = 6.49, fig.cap = "NMDS ordination based on Sørensen dissimilarity of the species composition of 288 plots on dike grasslands over four years after sowing the seed mixtures (black squares).  In addition, 98 positive and negative reference plots were included from older dike grasslands in the surroundings [@bauer2023] and six plots from sPlotOpen [@Sabatini.2021].  The circles show the standard error of the groups. 2D stress: 0.21."}
knitr::include_graphics(
  here::here("outputs", "figures", "figure_6_nmds_800dpi_16.5x16cm.tiff")
  )
```
